Proposed Solution

### 2016-11-12 Ennan-Proposal/arch.tex
Grammatical changes.:

We propose to build \app, an automatic verification framework for 
software configuration files, by exploring further the insights we 
obtained when building ConfigC. Figure~\ref{fig-overview} presents
a typical \app verification workflow which contains three steps:
translation into an intermediary representation, a specification 
learning, and checking the correctness of a given configuration file.

@@

\paragraph{Learning Specifications.}
Similarly as before, we start with an assumption 
that we are given a number of 
configuration files belonging to the same system (\eg, MySQL or Apache).
Additionally, we assume that files in this data set are 
not necessarily correct, but if there are errors they appear only in some
file. We then translate that dataset into a more structured
and typed intermediate representation, which follows
our defined language model (cf. Sec.~\ref{sec:lang}).
Since the type of an entry cannot be fully determined from 
the entry value, we introduce {\em probabilistic types}, which is
a more flexible type notion: to a indefinite keyword it 
assigns a list of possible types together with their probability 
distribution. The learner module employs a collection of learning
 algorithms to generate various rules and constraints.
It uses type-annotated templates to infer the rules. In addition, 
there are algorithms for detecting ordering errors and missing entry
errors, which do not depend on templates. However, this time, 
since the input set is not necessarily correct, the learned rules are
also annotated with the probability indicating the likelihood of being 
correct.

@@

\paragraph{Correctness Checking.}
The checker takes as input a configuration files and reports 
it the file adheres to the learned specification. In addition, it 
will also check if the keyword values fall into a certain range and they are not significantly different than the value usually used.
The checker generates a report (as shown in Sec.~\ref{sec:prelim}) about 
found errors.

>>>>

We propose to build \app, an automatic verification framework for 
software configuration files, by exploring further the insights we 
obtained when building ConfigC. Figure~\ref{fig-overview} presents
a typical \app verification workflow which contains three steps:
translation into an intermediary representation, learning of a specification,
and checking the correctness of a given configuration file.

@@

\paragraph{Learning Specifications.}
As with ConfigC, we start with an assumption 
that we are given a number of 
configuration files belonging to the same system (\eg, MySQL or Apache).
Additionally, we assume that files in this dataset are 
not necessarily correct, but if there are errors they appear only in some
files. We then translate the dataset into a more structured
and typed intermediate representation, which follows
our defined language model (cf. Sec.~\ref{sec:lang}).
Since the type of an entry cannot be fully determined from 
the entry value, we introduce {\em probabilistic types}, which are
a more flexible type notion: to an indefinite keyword it 
assigns a list of possible types, along with their probability 
distribution. The learner module employs a collection of learning
 algorithms to generate various rules and constraints.
It uses type-annotated templates to infer the rules. In addition, 
there are algorithms for detecting ordering errors and missing entry
errors, which do not depend on templates. However, this time, 
since the input set is not necessarily correct, the learned rules are
also annotated with the probability indicating the likelihood of being 
correct.

@@

\paragraph{Correctness Checking.}
The checker takes as input a configuration file and reports 
if the file adheres to the learned specification. In addition, it 
will also check that the keyword values fall into a certain range and they are not significantly different than the value usually used.
The checker generates a report (as shown in Sec.~\ref{sec:prelim}) about 
found errors.

### 2016-11-12 Ennan-Proposal/language.tex
Grammatical changes.:

There are several types of configuration 
files and each has different representation. Our goal is to find a good 
intermediary representation that will be language-agnostic. In general,
one can complain that a design of configuration files is pretty low 
level and that we need a new programming language for them. We agree with 
that assertion, and actually our intermediary representation can be seen
as a new programming paradigm for writing configuration files, but this
is not the focus of this proposal. Previously, Huang {\em et al.}~\cite{huang15confvalley} proposed a 
language, ConfValley, to validate 
whether given configuration files meet administrators' specifications. 
However, ConfValley cannot check for misconfiguration checking 
capability, since it is only a library. In ConfValley the administrator 
still needs to write specifications manually, which is an error-prone
process. On the contrary, \app does not require users to manually
write anything.

@@

Translating or parsing is system dependent. In other words, for MySQL
and HDFS, we need to develop different parsers to handle each of them,
respectively. Configuration files mainly consists of assignments of the form {\tt {keyword = value}}. Our first attempt was to simply
translate every key-value entry {\tt {k = v}} into a triple $(k, v, \tau)$, where $\tau$ is a type of 
$v$. However, sometimes we could not fully determine the type of key 
based on a single example value. For this reason, we introduced {\emph {probabilistic types}}.

@@

In \app, the set $\mathcal{T}$ should contains strings, integers, file paths, 
sizes, and IP addresses. With every type, we associate a list of templates 
that are used to learn the rules about those files. Table~\ref{table:kysymys} contains
the most important types and templates.

@@

In general, the templates works as follows: if there are two entries ${\tt {k1 = v1}}$ and 
${\tt {k2 = v2}}$, and let $t(X, Y)$ be a template that can be applied to those values (w.r.t. their types).
If $t(v1, v2)$ holds, \ie, the template condition is valid for those concrete values, then we will add a rule
$t(k1, k2)$ to a list of potentially correct specifications. Note that the rule expresses a relation between keywords, and not values.

>>>>

There are several types of configuration 
files, and each has a different representation. Our goal is to find a good 
intermediary representation that will be language-agnostic. In general,
one could argue that the design of configuration files is pretty low 
level, and that we need a new programming language for them. We agree with 
that assertion, and actually our intermediary representation can be seen
as a new programming paradigm for writing configuration files, but this
is not the focus of this proposal. Previously, Huang {\em et al.}~\cite{huang15confvalley} proposed a 
language, ConfValley, to validate 
whether given configuration files meet administrators' specifications. 
However, ConfValley cannot check for misconfiguration checking 
capability, since it is only a library. In ConfValley the administrator 
still needs to write specifications manually, which is an error-prone
process. On the contrary, \app does not require users to manually
write anything.

@@

Translating or parsing is system dependent. In other words, for MySQL
and HDFS, we need to develop different parsers.
Configuration files mainly consists of assignments of the form {\tt {keyword = value}}. Our first attempt was to simply
translate every key-value entry {\tt {k = v}} into a triple $(k, v, \tau)$, where $\tau$ is a type of 
$v$. However, sometimes we could not fully determine the type of key 
based on a single example value. For this reason, we introduced {\emph {probabilistic types}}.

@@

In \app, the set $\mathcal{T}$ should contain strings, integers, file paths, 
sizes, and IP addresses. With every type, we associate a list of templates 
that are used to learn the rules about those files. Table~\ref{table:kysymys} contains
the most important types and templates.

@@

In general, the templates works as follows: if there are two entries ${\tt {k1 = v1}}$ and 
${\tt {k2 = v2}}$, such that $t(X, Y)$ is a template that can be applied to those values (w.r.t. their types).
If $t(v1, v2)$ holds, \ie, the template condition is valid for those concrete values, then we will add a rule
$t(k1, k2)$ to a list of potentially correct specifications. Note that the rule expresses a relation between keywords, and not values.

### 2016-11-12 Ennan-Proposal/motivation.tex
Grammatical changes.:

Configuration errors are one of the most important root causes of
today's software system failures~\cite{xu15systems, yin11anempirical}.
We read in the news that recently there was a problem in accessing  
Facebook and Instagram~\cite{mashableNews}, 
and a Facebook spokeswoman reported that 
this was caused by a change to the site's configuration systems.
In a recent software system failures study~\cite{yin11anempirical},
researchers revealed that about 31\% of system failures were caused by 
configuration errors, which is higher than the percentage of
failures resulting from program bugs (20\%). 
%(which and only 20\% were caused by bugs in program code 
%While program verification is mostly focused on detecting errors 
%in code, in their empirical study 
%Yin {\em et al.}~\cite{yin11anempirical} report
%that about 31\% of system failures were caused by configuration errors problems and only 20\% were caused by bugs in program code. 
Configuration errors are commonly known in literature 
under the name misconfigurations.

@@

\para{Example~1: Ordering errors.} 
When a user configures PHP  to run with the Apache HTTP Server, most 
likely the user will take some already existing configuration files and 
adapt them to suit her needs. The configuration file might contain, among 
others,  the following lines:
\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
extension = mysql.so
...
extension = recode.so
\end{lstlisting} 
In that case the configuration file will cause the Apache server to 
fail to start due to a segmentation fault error. 
This is because, when using PHP in Apache, the extension {\tt mysql.so} 
depends on {\tt recode.so}, and their relative ordering
is crucial. This is an example of so-called {\em ordering error}.
Yin {\em et al.} report that ordering errors widely exist in
many system configurations, \eg, PHP and MySQL,
and typically lead to multiple system crash events.
However, no existing tool in the systems research can effectively solve 
or detect this problem~\cite{zhang14encore, xu15systems, xu13do}.

\para{Example~2: Fine-grained value correlation error.} 
Next example also comes from a discussion on 
StackOverflow~\cite{correlation}.
The user has configured her MySQL as in the following:
\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
key_buffer_size = 384M
max_heap_table_size = 128M
max_connections = 64
thread_cache_size = 8
...
sort_buffer_size = 32M
join_buffer_size = 32M
read_buffer_size = 32M
read_rnd_buffer_size = 8M
...
\end{lstlisting} 
The user then complained that her MySQL load was very high, causing the website's
response speed to be very slow.
In this case, {\tt key\_buffer\_size} is used by all the threads
cooperatively, while {\tt join\_buffer} and {\tt sort\_buffer} are 
created by each thread for private use; thus, the maximum amount
of used key buffer, \ie, {\tt key\_buffer\_size}, should be larger than 
{\tt join|sort\_buffer\_size} * {\tt max\_connections}. 
Clearly, in the above example, it does not hold, 
so this misconfiguration causes MySQL to load very slowly.
This type of error is more sophisticated than the simple value correlation that some tools can detect~\cite{yin11anempirical, zhang14encore}.

@@

We believe there are two main obstacles 
why we cannot simply apply the existing automatic 
tools and techniques to verification of configuration files are:
\begin{itemize}
\item a lack
of a specification describing properties of configuration files
\item a program structure of configuration files -- they
are mainly a sequence of entries assigning some value to system
variables (called {\emph {keywords}}). 
\end{itemize}
The language in which configuration files are written does 
not adhere to a specific grammar or syntax. In particular, the
entries in configuration files are untyped. Moreover, there are surprisingly few rules specifying constraints on entries and there
is no explicit structure policy for the entries.
We believe that those are the reasons why there is no automated verification of configuration 
files although the system community expressed that that would be highly
desirable~\cite{wang04automatic, zhang14encore, xu15systems}.

@@

The goal of this proposal is to develop a fully {\bf {automated 
verification  framework for general software configurations}}. We plan to
overcome the above obstacles by first automatically inferring a
specification for configuration files. It is unrealistic to expect the 
users to write an entire specifications for configuration files on their own. 
This process can easily lead to incomplete or even contradictory 
specifications. Instead, we will learn specification from 
a large sample of 
configuration files. A learning process will take as input this 
sample. The process will be language-agnostic and should work for any kind 
of configuration files,  but all of the files in the sample need to be of 
the same kind (such as MySQL or 
HTTPD configuration files). From that sample, we will learn an abundant set of rules 
specifying various properties that hold on the given sample. The rules, in general, 
specify which properties keywords in configuration files need to satisfy. One can see this learning process as 
a way of deriving  a specification for configuration files. 
It is also hard to talk here about a complete specification, but 
still having some specification is better than none, and we plan to 
increase the preciseness of a specification as we gain a better 
understanding of the formalism needed for its description.
Having a specification, we can efficiently check 
the correctness of the configuration files of interest and detect 
potential errors. Errors are reported if the configuration file does not 
adhere to the derived specification.

@@

Building such an automatic verification framework for
configuration files requires addressing several challenges. 
First, in the process of inferring a specification, we have to 
analyze mainly with an untyped, unstructured sequence of assignments.
Thus, we need to develop a suitable language model. We do that by 
``guessing'' a type of keywords and then deriving formulas that
describe relationships between these keywords. However, the
type of a keyword cannot always be fully determined 
from a single value. 
An entry {\tt general\_log = 1} in a MySQL configuration file assigns an integer to the 
keyword {\tt general\_log}. However, 1 here is a Boolean variable,
which denotes that there will be a general log file.
Another example, which often appears in practice, shows how keyword names and 
their ``types'' can easily lead to an error. Consider the
following entry {\tt general\_log = /var/log/mysql/mysql.log}. Although this statement 
alone might look correct, this is actually a typing error and as a result MySQL log cannot be correctly written.

Second, we will learn patterns describing keywords and their relations. We will associate with each type a set of very general templates. The user does not need to provide any templates -- they are internally associated to the types.
Nevertheless, in addition to those general templates, we still need specific algorithms to learn
rules that cannot be easily templated (such as ordering rules).

>>>>

Configuration errors are one of the most important root causes of
today's software system failures~\cite{xu15systems, yin11anempirical}.
Recently, there was a problem in accessing  
Facebook and Instagram~\cite{mashableNews}, 
and a Facebook spokeswoman reported that 
this was caused by a change to the site's configuration systems.
In a recent software system failures study~\cite{yin11anempirical},
researchers revealed that about 31\% of system failures were caused by 
configuration errors, which is higher than the percentage of
failures resulting from program bugs (20\%). 
%(which and only 20\% were caused by bugs in program code 
%While program verification is mostly focused on detecting errors 
%in code, in their empirical study 
%Yin {\em et al.}~\cite{yin11anempirical} report
%that about 31\% of system failures were caused by configuration errors problems and only 20\% were caused by bugs in program code. 
Configuration errors are commonly known in literature 
under the name misconfigurations.

@@

\para{Example~1: Ordering errors.} 
When a user configures PHP  to run with the Apache HTTP Server, most 
likely the user will take some already existing configuration files and 
adapt them to suit her needs. The configuration file might contain, among 
others,  the following lines:
\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
extension = mysql.so
...
extension = recode.so
\end{lstlisting} 
In this case, the configuration file will cause the Apache server to 
fail to start due to a segmentation fault error. 
This is because, when using PHP in Apache, the extension {\tt mysql.so} 
depends on {\tt recode.so}, and their relative ordering
is crucial. This is an example of an {\em ordering error}.
Yin {\em et al.} report that ordering errors widely exist in
many system configurations, \eg, PHP and MySQL,
and typically lead to multiple system crash events.
However, no existing tool in the systems research area can effectively solve 
or detect this problem~\cite{zhang14encore, xu15systems, xu13do}.

\para{Example~2: Fine-grained value correlation error.} 
Our next example also comes from a discussion on 
StackOverflow~\cite{correlation}.
The user has configured her MySQL as follows:
\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
key_buffer_size = 384M
max_heap_table_size = 128M
max_connections = 64
thread_cache_size = 8
...
sort_buffer_size = 32M
join_buffer_size = 32M
read_buffer_size = 32M
read_rnd_buffer_size = 8M
...
\end{lstlisting} 
The user complained that her MySQL load was very high, causing the website's
response speed to be very slow.
In this case, {\tt key\_buffer\_size} is used by all the threads
cooperatively, while {\tt join\_buffer} and {\tt sort\_buffer} are 
created by each thread for private use; thus, the maximum amount
of used key buffer, \ie, {\tt key\_buffer\_size}, should be larger than 
{\tt join|sort\_buffer\_size} * {\tt max\_connections}. 
Clearly, in the above example, this does not hold, 
so this misconfiguration causes MySQL to load very slowly.
This type of error is more sophisticated than the simple value correlation that some tools can detect~\cite{yin11anempirical, zhang14encore}.

@@

We believe there are two main obstacles 
to simply applying the existing automatic 
tools and techniques to verification of configuration files:
\begin{itemize}
\item the lack
of a specification describing properties of configuration files
\item the structure of configuration files -- they
are mainly a sequence of entries assigning some value to system
variables (called {\emph {keywords}}). 
\end{itemize}
The language in which configuration files are written does 
not adhere to a specific grammar or syntax. In particular, the
entries in configuration files are untyped. Moreover, there are surprisingly few rules specifying constraints on entries, and there
is no explicit structure policy for the entries.
We believe these to be the reason for the %that those are the reasons why there is no
lack of automated verification of configuration 
files,% although the system community expressed that that would be highly desirable
despite the systems community desires for such verification~\cite{wang04automatic, zhang14encore, xu15systems}.

@@

The goal of this proposal is to develop a fully {\bf {automated 
verification  framework for general software configurations}}. We plan to
overcome the above obstacles by first automatically inferring a
specification for configuration files. It is unrealistic to expect the 
users to write an entire specifications for configuration files on their own. 
This process can easily lead to incomplete or even contradictory 
specifications. Instead, we will learn specification from 
a large sample of 
configuration files,%A learning process will take as input this sample.
which will be taken by the learning process as input.
The process will be language-agnostic and should work for any kind 
of configuration files,  but all of the files in the sample need to be of 
the same kind (such as MySQL or 
HTTPD configuration files). From that sample, we will learn an abundant set of rules 
specifying various properties that hold on the given sample. The rules, in general, 
specify which properties keywords in configuration files need to satisfy. One can see this learning process as 
a way of deriving  a specification for configuration files. 
It is hard to talk here about a complete specification, but 
still having some specification is better than none, and we plan to 
increase the preciseness of a specification as we gain a better 
understanding of the formalism needed for its description.
With a specification, we can efficiently check 
the correctness of the configuration files of interest and detect 
potential errors. Errors are reported if the configuration file does not 
adhere to the derived specification.

@@

Building such an automatic verification framework for
configuration files requires addressing several challenges. 
First, in the process of inferring a specification, we have to 
analyze mainly with an untyped, unstructured sequence of assignments.
Thus, we need to develop a suitable language model. We do that by 
``guessing'' a type of keywords and then deriving formulas that
describe relationships between these keywords. However, the
type of a keyword cannot always be fully determined 
from a single value. 
An entry {\tt general\_log = 1} in a MySQL configuration file assigns an integer to the 
keyword {\tt general\_log}. However, 1 here is a Boolean variable,
which denotes that there will be a general log file.
Another example, which often appears in practice, shows how keyword names and 
their ``types'' can easily lead to an error. Consider the
entry {\tt general\_log = /var/log/mysql/mysql.log}. Although this statement 
alone might look correct, this is actually a typing error which will prevent the MySQL log from being correctly written.

Second, we will learn patterns describing keywords and their relations. We will associate with each type a set of very general templates. The user does not need to provide any templates -- they are internally associated to the types.
In addition to those general templates, we still need specific algorithms to learn
rules that cannot be easily templated (such as ordering rules).

### 2016-11-12 Ennan-Proposal/prelim.tex
Grammatical changes.:

From ConfigC we drew the main inspiration for this proposal. We now briefly
outline how does ConfigC work. It first automatically
analyzes a dataset of correct configuration files to derive
 rules for describing a specification. Before that process even starts,
we identified several basic types, 
such Boolean, Integer, File. With each of these types we associated a 
list of templates. We then analyze the given training data set of 
correct configuration files and derive rules describing variable                                                                                                                                                                                                                                                                                                                                                                                                                       
relations. We illustrate how is this done on two fragments of 
configuration files given in Fig.~\ref{fig:twoFiles}.  When analyzing
a file, we first assign a type to every 
keyword. After that we instantiate each type-annotated template with 
concrete keywords and we save the learned set 
of rules. For instance, with the integer type we only associated comparison templates ($X < Y, X = Y, \ldots$). After 
analyzing File\_1, the set of learned rules will contain the following rules:
\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
max_connections=300
mysql.max_persistent=200
max_connections > mysql.max_persistent
\end{lstlisting}
The set of learned rules is changing with every file that we analyze: contradicting 
files are removed and new rules are added. After analyzing File\_2 the rule \texttt{max\_connections = 300} is removed. In practice, this process is done 
in parallel.

@@

Additionally to the described process, we also developed algorithms for 
the misconfigurations that cannot easily be templated. All together, 
ConfigC can detect the following errors:
missing entries, ordering errors, type errors and
simple value correlations. Once this preprocessing of training data is 
done, the resulting language model, 
together with accompanying rules, 
is used to detect errors in new configuration files given by the user.

Running ConfigC on Example~1 from 
Sec.~\ref{sec:intro-examples} returns the following output:
\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
ORDERING ERROR: Expected extension "recode.so" BEFORE 
extension "mysql.so"
\end{lstlisting} 
ConfigC could not detect an error present in Example~2 since it can detect 
only simple comparison-based relations.

@@

\item ConfigC works on the premise that the training dataset consists 
only of correct files, which is hard to achieve in practice. In the 
prototype we manually checked every file in the prototype. Clearly, this 
approach will not scale in practice. There exist a large set of 
real-world misconfigurations~\cite{configdataset}. Nevertheless, the 
errors are distributed through the files and do not all appear at the 
same spot. We believe that it should be possible to construct a correct
specification from the rules that hold in a significant majority of the 
files.

\item A language model used in ConfigC cannot handle a simple version of 
the {\tt {if-then}} command that sometimes appears in some configuration
files (such as Apache HTTPD). We already pointed out some issues with 
parsing and possible wrong typing. We need to develop a more 
accurate model which will be a uniform representation for diverse
  configuration files.

\item ConfigC offers only a limited number of templates to to detect 
correlation errors on keywords. It can detect, for example, 
keyword comparisons, but in practice many software outages were 
caused by more complex correlations (also called
  fine-grained correlations~\cite{correlation}). As an illustration,
  ConfigC cannot find an error in Example~2 in 
Sec.~\ref{sec:intro-examples}. However, to detect more complex rules, we will need to use tools like SMT solvers \cite{z3, cvc4}.

\item ConfigC cannot check for anomalies in a value set for one particular keyword. For example,
  setting a parameter, which relates memory in MySQL configuration 
  files, too large can cause exhausting the RAM and causing extreme 
  slowness or even a crash. Such an anomalous value does not violate any
  previously mentioned constraints (such as type errors or ordering errors), but yet 
  it makes system behave wrongly.

>>>>

From ConfigC we drew the main inspiration for this proposal. We now briefly
outline how ConfigC works. It first automatically
analyzes a dataset of correct configuration files to derive
 rules for describing a specification. Before that process even starts,
we identified several basic types, 
such Boolean, Integer, File. With each of these types we associated a 
list of templates. We then analyze the given training data set of 
correct configuration files and derive rules describing variable                                                                                                                                                                                                                                                                                                                                                                                                                       
relations. We illustrate how is this done on two fragments of 
configuration files given in Fig.~\ref{fig:twoFiles}.  When analyzing
a file, we first assign a type to every 
keyword. After that we instantiate each type-annotated template with 
concrete keywords and we save the learned set 
of rules. For instance, with the integer type we only associated comparison templates ($X < Y, X = Y, \ldots$). After 
analyzing File\_1, the set of learned rules will contain the following rules:
\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
max_connections=300
mysql.max_persistent=200
max_connections > mysql.max_persistent
\end{lstlisting}
The set of learned rules changes with every analyzed file: contradicting 
rules are removed and new rules are added. After analyzing File\_2 the rule \texttt{max\_connections = 300} is removed. In practice, this process is done 
in parallel.

@@

Additionally, we also developed algorithms for 
misconfigurations that cannot easily be templated. All together, 
ConfigC can detect the following errors:
missing entries, ordering errors, type errors and
simple value correlations. Once this preprocessing of training data is 
done, the resulting language model, 
together with accompanying rules, 
is used to detect errors in new configuration files given by the user.

Running ConfigC on Example~1 from 
Sec.~\ref{sec:intro-examples} returns the following output:
\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
ORDERING ERROR: Expected extension "recode.so" BEFORE 
extension "mysql.so"
\end{lstlisting} 
ConfigC could not detect the error present in Example~2 since it can detect 
only simple comparison-based relations.

@@

\item ConfigC works on the premise that the training dataset consists 
only of correct files, which is hard to achieve in practice. In the 
prototype we manually checked every file in the prototype. Clearly, this 
approach will not scale. There exist a large set of 
real-world misconfigurations~\cite{configdataset}. Nevertheless, the 
errors are distributed through the files and do not all appear at the 
same spot. We believe that it should be possible to construct a correct
specification from the rules that hold in a significant majority of the 
files.

\item The language model used in ConfigC cannot handle a simple version of 
the {\tt {if-then}} command that appears in some configuration
files (such as Apache HTTPD). We already pointed out some issues with 
parsing and possible incorrect typing. We need to develop a more 
accurate model which will be a uniform representation for diverse
  configuration files.

\item ConfigC offers only a limited number of templates to to detect 
correlation errors on keywords. It can detect, for example, 
keyword comparisons, but in practice many software outages are 
caused by more complex correlations (also called
  fine-grained correlations~\cite{correlation}). As an illustration,
  ConfigC cannot find an error in Example~2 in 
Sec.~\ref{sec:intro-examples}. However, to detect more complex rules, we will need to use tools like SMT solvers \cite{z3, cvc4}.

\item ConfigC cannot check for anomalies in a value set for one particular keyword. For example,
  setting a parameter, which relates memory in MySQL configuration 
  files, too large can exhaust the RAM, leading to extreme 
  slowness or even a crash. Such an anomalous value does not violate any
  previously mentioned constraints (such as type errors or ordering errors), but 
  it makes system behave incorrectly.
